A Minimal Demo of \texttt{glyphmaps}

### 2012-06-04 paper/demo.Rnw
tweaked geom_coxcomb. Wrote paper

\maketitle
This document demonstrates the basic features of the \texttt{glyphmaps} package (name may change). \texttt{glyphmaps} was written to create plots like the ones below. Each plot is made with \texttt{glyphmaps}. They recreate Figures 8 and 10a from \citet{wickham2012glyph}. To run the examples in this document please download the \texttt{glyphmaps} package with the code below.

@@

<<glyphmaps-fig-8>>=
p <- ggplot(seasons) + 
  map_us +
  glyph(
    geom_line(aes(x = time, y = pred)), 
    major = aes(lon[1], lat[1]), glyph.by = "stn", 
    ref = ref_box(aes(fill = avg)))
@

<<glyph maps merged>>=
@

@@

<<boring-random>>=
library(devtools)
load_all("ggplyr")
@

@@

<<boring-random>>=
set.seed(1121)
(x=rnorm(20))
mean(x);var(x)
@

>>>>

\maketitle
This document demonstrates the basic features of the \texttt{glyphmaps} package (name may change). \texttt{glyphmaps} was written to create plots like the ones below, which recreate plots similar to those in \citet{wickham2011split} and \citet{wickham2012glyph}. Each plot is made with \texttt{glyphmaps}. To run the examples in this document please download the \texttt{glyphmaps} package with the code below. (Note: Install won't work until I finish documenting the namespace. But cloning and load_all() DOES work.)

@@

<<glyphmaps-fig-8>>=
ggplot(seasons) + map_us + 
  grid(geom_line(aes(x = time, y = pred)), 
    grid.aes = aes(lon, lat), x.nbin = 58, y.nbin = 25,
    ref = ref_box(aes(fill = avg), alpha = 0.2, color = NA))
ggplot(nasa) +  map_nasa +
  glyph(geom_star(aes(r = ozone, angle = date, x = 0, y = 0, fill = mean(temperature))), 
  major.aes = aes(long[1], lat[1]), glyph.by = c("long", "lat"))
@

<<glyph-maps-merged>>=
@

@@

@@
